manuscript

### 2023-12-01 scripts/manuscript.qmd
Learned another line of code from this group

>>>>

Wow impressive specification of your figure here. I always struggle with the detailed ggplot arguments to get the vis I want exactly. This usually takes a lot of time and digging through code manuals (web pages). I commend you!! (and saved the ` geom_text(x = 30, y = 4, label = sprintf)...` code for potential future use.)
